Papers

### 2023-05-16 quarto/papers.qmd
update

* Z. Zeng, C. Hawkins, M. Hong, **A. Zhang**, N. Pappas, V. Singh, and S. Zheng<br>
<a href="https://arxiv.org/abs/2305.04241" target="_blank">Vcc: Scaling Transformers to 128K Tokens or More by Prioritizing Important Tokens</a><br>
*"Only a small subset of tokens are relevant to the output."*
In *arXiv*, 2023<br>

>>>>

* Z. Zeng, C. Hawkins, M. Hong, **A. Zhang**, N. Pappas, V. Singh, and S. Zheng<br>
<a href="https://arxiv.org/abs/2305.04241" target="_blank">Vcc: Scaling Transformers to 128K Tokens or More by Prioritizing Important Tokens</a><br>
*"Only a small subset of tokens are important to the output."*
In *arXiv*, 2023<br>
